---
title: "Assessment 1"
output: html_document
---
## R basics:
```{r, echo=FALSE}
```


The following vector represents the number of world-wide deaths from corona in the last 60 days. 
```{r}
deaths = c(16,24,26,26,37,38,43,45,46,54,58,58,64,64,65,66,67,73,73,73,81,83,85,86,89,97,97,98,100,102,105,106,107,108,113,117,121,122,136,143,143,146,158,198,228,271,332,353,405,447,642,687,817,972,1079,1356,1625,1629,1873,2381)
```


1. Write code that computes a vector called 'total' of the same length representing the cumulative number of deaths until each day. <br>
    **Solution:**
```{r}
total <- c(1:length(deaths))
total <- total*0
for (i in 1:length(deaths)) {
  total[i] <- sum(deaths[1:i])
}

print(total)
```

2. Write code that finds all the days at which there was no increase in deaths compared to the previous day. <br>
    **Solution:**
```{r}
no_increase <- c()
for (i in 2:length(deaths)) {
  if(deaths[i-1] == deaths[i]){
  no_increase <- append(no_increase,i) }
}
print(no_increase)
```


3. Explain in a couple of sentences what does the vector v represent when we write: <br>
`v <- round(total[-1] / head(total, -1) - 1, 3)` <br>
    **Solution:**  
    
`**1)** each number in the vector v is the ratio between the number of deaths 
 on day i and the number of deaths on the day i-1  `

4. Find the **relative** increase in deaths between the total number of deaths in day 59 and day 60. Suppose that this relative increase will remain the same for each day of the next 40 days. Compute the total number of deaths on day 100 <br>
    **Solution:**
```{r}
incr <- total[60]/total[59]
total_incr <- incr^40
day_100 <- total[60]*total_incr
print(day_100)
```


5. Compute `1 + 1/2^2 + 1/3^2 + ... 1/100^2`. Compute also $\pi^{2}/6$ and calculate the difference. 
Repeat now with `1 + 1/2^2 + 1/3^2 + ... 1/1000^2`. Is the difference smaller?
<br>
    **Solution:**
```{r}
i <- c(1:100)
q <- c(1/(i^2))
print(sum(q))
p <- (pi^2)/6
print(p)
print(p-sum(q))
new_i <- c(1:1000)
new_q <- c(1/(new_i^2))
print(sum(new_q))
print(p - sum(new_q))
if(p-sum(new_q) < p-sum(q)){
  print("yes")
} else { print("no")}
```