---
title: "Assessment 4"
author: 'itay hadash'
date: "May 10th, 2020"
output:
  html_document: default
  pdf_document: default
---

## Assessment 4:   

1. Write a function called *'trim.mean'* that takes as input a vector of numbers and a parameter alpha, and returns 
the alpha-trimmed mean of the vector. 
   The function should check that the value of alpha is in the correct range.  
   You can compare to R function mean( , trim= ) to see that results are similar.  
   Hint: The functions floor() and ceiling() round up to the nearest integer below and above a certain value.   

    **Solution:**
```{r}
trim.mean <- function(vec,alpha){
    if (alpha>0.5 || alpha<0) {
        return(F)
    }
    vec <- vec[order(vec)]
    a <-min(floor((length(vec)-1))/2,floor(alpha*length(vec)))
    trim_vec <- vec[c((a+1):(length(vec)-a))]
    trim_m <- (1/(length(vec)-2*a))*sum(trim_vec)
    return(trim_m)
}
# This function performs alpha mean trim - orderes the 'vec' and trims a ratio
  # of `alpha` from either sides of the vector.
  #@param vec: vector, a list of numbers 
  #@param alpha: double, a number between 0 and 0.5 (including)
  
```

2. Write a function called *'my.mad'* that takes as input a vector of numbers, and returns 
the corrected median-absolute-deviation. That is, the estimator should be corrected such that 
for Normal data as $n \to \infty$ the estimator converges to $\sigma$ the standard deviation. 
You can compare to R function mad() to see that results are similar.  


    **Solution:**
```{r}
# robust standard deviation estimate
my.mad <- function(x){
  MA<- median(abs(x-median(x)))
  return(MA/qnorm(0.75))
  
}
```
  

3. Analyze the world fertility rate data (average number of children per woman) obtained from the gapminder dataset which contains demographic data on world countries in different years:
a. Create a new variable containing the fertility in 1960 for every country and use it for the next sub-questions.
b. Compute and show the mean and standard deviation for the fertility rate in 1960.   
c. Compare the fertility distribution to the Normal distribution by plotting together the data-density vs. the matching Normal density with the same first two moments. 
d. Make a qq-plot comparing the data distribution and the above Normal distribution.    
e. Does the distribution have a heavy tail? Is it skewed?  report the skewness and kurtosis parameters. 
f. Compute robust estimates [trimmed-mean with $\alpha=0.05$, inter-quantile-range or MAD]; Compare these to the mean and standard deviation.

    **Solution:**
```{r}
library(dslabs)
library(tidyverse)
library(e1071) # has skewness and kurtosis functions 
library(ggplot2)
data(gapminder) # load dataset
##a##
gap <- gapminder
gap_1960 <- gap %>% filter(year == 1960)
gap_1960 <- gap_1960[c(1,5)]
gap1960 <- gap_1960[,2] #a new variable containing the fertility in 1960 for every country
##b##
mean1 <- mean(gap1960)
mean1
sd1 <- sd(gap1960)
sd1
##c##
normi <- data.frame(x=seq(-4,4,len = 50)*sd1 +mean1) %>% mutate(density=dnorm(x,mean1,sd1))
k <- ggplot(data=gap_1960,aes(gap1960)) + geom_density(fill="#0099FF") + geom_line(data=normi,aes(x,density),lwd =2) + labs(title = "normal dis vs data dis",x="fertility rate" )
k
##d##
q <- ggplot(data=gap_1960,aes(sample = gap1960)) + stat_qq() + stat_qq_line()
q
##e##
kurtosis(gap1960)
print("there are long tails")
skewness(gap1960)
print("there is a left tail")
##f##
tm <-trim.mean(gap1960,0.05)
n_mad <- mad(gap1960)
print("trim mean")
tm
print("the gap between the trim mean and mean")
tm-mean1
# we can see there is a gap between the trim mean and the mean and it is cased by 
# the mean of those variables was lower than the total mean 
# there for subtracting tham increase the thri mean
print("the MAD")
n_mad
print("the gap between the MAD and sd")
n_mad - sd1
# we can see there is a gap between the MAD and the SD and it is cased by
# because the MAD is based on the distance from the median(which is 6.19) and SD is based on the distance from the mean(which is 5.48)
# 
```
